---
title: "Assignment 3"
output: html_document
date: '2022-07-24'
---
# Explanation
#### Written with Rmarkdown. The results and graphs are hidden, only the code is shown.
#### I've done DiD regressions on multiple time periods before with stata, using simple covariates on time and individuals. I was shocked at the level of sophistication of this R package.

#### Whether it works or not, I upgraded R. If we install the did package directly it will report an error, we need to install the "DRDID" package first.
#### In the "Using the Callaway and Sant'Anna (202) framework"section, the code "ata_CS_never <- map_dfr(1:nrep, run_CS_never)" reports an error, and I really don't know how to handle it, so I have to choose to skip all the relevant parts.

#### What's worse is that,even though the developer has indicated that functions related to simulated data have already been  available in https://github.com/bcallaway11/did/issues/44, I was unable to generate simulated data successfully in all places involving" build_sim_dataset()" or" reset.sim()".
#### Even if I refer to the original vignettes.Rmd on github and generate simulated data, it doesn't match with the developer's result even in rows.

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
```{r gh-installation, eval = FALSE}
devtools::install_github("pedrohcgs/DRDID")
devtools::install_github("bcallaway11/did")
```
```{r message=FALSE,results='hide',fig.show='hide'}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages("tidyverse")
install.packages("lfe")
install.packages("fastDummies")
install.packages("ggthemes")
```
```{r message=FALSE,results='hide',fig.show='hide'}
library(tidyverse)
library(lfe)
library(fastDummies)
library(ggthemes)
library(did)
library(DRDID)
theme_set(theme_clean() + theme(plot.background = element_blank()))
iseed  = 20201221
nrep <- 100  
true_mu <- 1
set.seed(iseed)
```
# Getting Started with the did Package
#### Examples with simulated data
Estimating Group-Time Average Treatment Effects
```{r message=FALSE,results='hide',fig.show='hide'}
set.seed(1814)
time.periods <- 4
sp <- reset.sim()
sp$te <- 0
sp$te.e <- 1:time.periods
dta <- build_sim_dataset(sp)
nrow(dta)
head(dta)
```
```{r message=FALSE,results='hide',fig.show='hide'}
example_attgt <- att_gt(yname = "Y",
                        tname = "period",
                        idname = "id",
                        gname = "G",
                        xformla = ~X,
                        data = dta
                        )
summary(example_attgt)
ggdid(example_attgt)
```
Other features of the did package
```{r message=FALSE,results='hide',fig.show='hide'}
agg.simple <- aggte(example_attgt, type = "simple")
summary(agg.simple)
agg.es <- aggte(example_attgt, type = "dynamic")
summary(agg.es)
ggdid(agg.es)

agg.gs <- aggte(example_attgt, type = "group")
summary(agg.gs)
ggdid(agg.gs)

agg.ct <- aggte(example_attgt, type = "calendar")
summary(agg.ct)
ggdid(agg.ct)
```
```{r message=FALSE,results='hide',fig.show='hide'}
example_attgt_altcontrol <- att_gt(yname = "Y",
                                   tname = "period",
                                   idname = "id",
                                   gname = "G",
                                   xformla = ~X,
                                   data = dta,
                                   control_group = "notyettreated"          
                                   )
summary(example_attgt_altcontrol)
```


#### An example with real data
```{r message=FALSE,results='hide',fig.show='hide'}
library(did)
data(mpdta)
head(mpdta)
mw.attgt <- att_gt(yname = "lemp",
                   gname = "first.treat",
                   idname = "countyreal",
                   tname = "year",
                   xformla = ~1,
                   data = mpdta,
                   )
summary(mw.attgt)
ggdid(mw.attgt, ylim = c(-.3,.3))

mw.dyn <- aggte(mw.attgt, type = "dynamic")
summary(mw.dyn)
ggdid(mw.dyn, ylim = c(-.3,.3))

mw.dyn.balance <- aggte(mw.attgt, type = "dynamic", balance_e=1)
summary(mw.dyn.balance)
ggdid(mw.dyn.balance, ylim = c(-.3,.3))

mw.attgt.X <- att_gt(yname = "lemp",
                   gname = "first.treat",
                   idname = "countyreal",
                   tname = "year",
                   xformla = ~lpop,
                   data = mpdta,
                   )
```

# Problems with two-way fixed-effects event-study regressions

#### Setup with all units being eventually treated and homogeneous treatment effect dynamics
Visualizing the DGP

```{r message=FALSE,results='hide',fig.show='hide'}
make_data <- function(nobs = 1000, 
                      nstates = 40) { 
  unit <- tibble(
    unit = 1:nobs,
    state = sample(1:nstates, nobs, replace = TRUE),
    unit_fe = rnorm(nobs, state/5, 1),
    mu = true_mu
    )
year <- tibble(
    year = 1980:2010,
    year_fe = rnorm(length(year), 0, 1)
  )
  treat_taus <- tibble(
    state = sample(1:nstates, nstates, replace = FALSE),
    cohort_year = sort(rep(c(1986, 1992, 1998, 2004), 10))
  )  
  expand_grid(unit = 1:nobs, year = 1980:2010) %>% 
    left_join(., unit) %>% 
    left_join(., year) %>% 
    left_join(., treat_taus) %>% 
    mutate(error = rnorm(nobs*31, 0, 1),
           treat = ifelse(year >= cohort_year, 1, 0),
           tau = ifelse(treat == 1, mu, 0),
           year_fe = year_fe + 0.1*(year - cohort_year)
    ) %>% 
    group_by(unit) %>% 
    mutate(tau_cum = cumsum(tau)) %>% 
    ungroup() %>% 
    mutate(dep_var = (2010 - cohort_year) + unit_fe + year_fe + tau_cum + error)
}
data <- make_data()
plot1 <- data %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) + 
  geom_line(alpha = 1/8, color = "grey") + 
  geom_line(data = data %>% 
              group_by(cohort_year, year) %>% 
              summarize(dep_var = mean(dep_var)),
            aes(x = year, y = dep_var, group = factor(cohort_year),
                color = factor(cohort_year)),
            size = 2) + 
  labs(x = "", y = "Value", color = "Treatment group   ") + 
  geom_vline(xintercept = 1986, color = '#E41A1C', size = 2) + 
  geom_vline(xintercept = 1992, color = '#377EB8', size = 2) + 
  geom_vline(xintercept = 1998, color = '#4DAF4A', size = 2) + 
  geom_vline(xintercept = 2004, color = '#984EA3', size = 2) + 
  scale_color_brewer(palette = 'Set1') + 
  theme(legend.position = 'bottom',
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12))  +
  ggtitle("One draw of the DGP with homogeneous effects across cohorts \n and with all groups being eventually treated")+
  theme(plot.title = element_text(hjust = 0.5, size=12))

plot1
```
Estimating dynamic treatment effects via TWFE event-study regressions
```{r message=FALSE,results='hide',fig.show='hide'}
keepvars <- c("`rel_year_-5`",  "`rel_year_-4`",  "`rel_year_-3`",  "`rel_year_-2`",
              "rel_year_0", "rel_year_1", "rel_year_2", "rel_year_3", "rel_year_4", "rel_year_5")

run_ES_DiD <- function(...) {
  
  data <- make_data()
  data <- make_data()
  data <- data %>% 
    mutate(rel_year = year - cohort_year) %>% 
    dummy_cols(select_columns = "rel_year") %>% 
    mutate(Pre = ifelse(rel_year < -5, 1, 0),
           Post = ifelse(rel_year > 5, 1, 0))
  mod <- lfe::felm(dep_var ~ Pre + `rel_year_-5` + `rel_year_-4` + `rel_year_-3` + `rel_year_-2` + 
                `rel_year_0` + `rel_year_1` + `rel_year_2` + `rel_year_3` + `rel_year_4` + 
                `rel_year_5` + Post | unit + year | 0 | state, data = data, exactDOF = TRUE)
  mod2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients)
    )
  
 es <-
   mod2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(-5:-2, 0:5)) %>% 
    select(t, estimate)
 es
}

data_classical <- map_dfr(1:nrep, run_ES_DiD)

colors <- c("True Effect" = "red", "Estimated Effect" = "blue")

ES_plot_classical <- data_classical %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  bind_rows(tibble(t = -1, avg = 0, sd = 0, lower.ci = 0, upper.ci = 0)) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* true_mu, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
  geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
  geom_line(aes(color = 'Estimated Effect'), size = 1) + 
  geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  ggtitle("TWFE event-study regression with binned end-points")+
  scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())

ES_plot_classical

```
```{r message=FALSE,results='hide',fig.show='hide'}
run_ES_DiD_sat <- function(...) {
  data <- make_data()
  data <- data %>% 
    mutate(rel_year = year - cohort_year)
  min_year <- min(data$rel_year)
  data <- data %>% 
    mutate(rel_year = rel_year - min_year) %>% 
    dummy_cols(select_columns = "rel_year")
  indics <- paste("rel_year", (1:max(data$rel_year))[-(-1 - min_year)], sep = "_", collapse = " + ")
  keepvars <- paste("rel_year", c(-5:-2, 0:5) - min_year, sep = "_")  
  formula <- as.formula(paste("dep_var ~", indics, "| unit + year | 0 | state"))
  mod <- felm(formula, data = data, exactDOF = TRUE)
  mod2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients)
    )
  
 es <-
   mod2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(-5:-2, 0:5)) %>% 
    select(t, estimate)
 es
}

data_sat <- map_dfr(1:nrep, run_ES_DiD_sat)

ES_plot_sat <- data_sat %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  bind_rows(tibble(t = -1, avg = 0, sd = 0, lower.ci = 0, upper.ci = 0)) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* true_mu, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
 geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
   geom_line(aes(color = 'Estimated Effect'), size = 1) + 
   geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  ggtitle("TWFE event-study regression with 'all' leads and lags")+
  scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())
    
ES_plot_sat
```
Using the Callaway and Sant’Anna (2021) framework
```{r message=FALSE,results='hide',fig.show='hide'}
run_CS <- function(...) {
  data <- make_data()
  mod <- did::att_gt(yname = "dep_var", 
                     tname = "year",
                     idname = "unit",
                     gname = "cohort_year",
                     control_group= "notyettreated",
                     bstrap = FALSE,
                     data = data,
                     print_details = FALSE)
  event_std <- did::aggte(mod, type = "dynamic")
  
  att.egt <- event_std$att.egt
  names(att.egt) <- event_std$egt

  broom::tidy(att.egt) %>% 
    filter(names %in% -5:5) %>% 
    mutate(t = -5:5, estimate = x) %>% 
    select(t, estimate)
}

data_CS <- map_dfr(1:nrep, run_CS)

ES_plot_CS <- data_CS %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* true_mu, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
  geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
   geom_line(aes(color = 'Estimated Effect'), size = 1) + 
   geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  ggtitle("Event-study-parameters estimated using Callaway and Sant'Anna (2021)\nComparison group: Not-yet-treated")+
    scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())

ES_plot_CS
```

#### Setup with a group that remains untreated at the end of the sampl
Visualizing the DGP
```{r message=FALSE,results='hide',fig.show='hide'}
make_data2 <- function(nobs = 1000, 
                      nstates = 40) {
  unit <- tibble(
    unit = 1:nobs,
    state = sample(1:nstates, nobs, replace = TRUE),
    unit_fe = rnorm(nobs, state/5, 1),
    mu = true_mu
  )
  
  year <- tibble(
    year = 1980:2010,
    year_fe = rnorm(length(year), 0, 1)
  )
  
  treat_taus <- tibble(
    state = sample(1:nstates, nstates, replace = FALSE),
    cohort_year = sort(rep(c(1986, 1992, 1998, 2004), 10))
  )
  
  expand_grid(unit = 1:nobs, year = 1980:2010) %>% 
    left_join(., unit) %>% 
    left_join(., year) %>% 
    left_join(., treat_taus) %>% 
    mutate(error = rnorm(nobs*31, 0, 1),
           treat = ifelse((year >= cohort_year)* (cohort_year != 2004), 1, 0),
           tau = ifelse(treat == 1, mu, 0),
           year_fe = year_fe + 0.1*(year - cohort_year)
    ) %>% 
    group_by(unit) %>% 
    mutate(tau_cum = cumsum(tau)) %>% 
    ungroup() %>% 
    mutate(dep_var = (2010 - cohort_year) + unit_fe + year_fe + tau_cum + error) %>%
    mutate(cohort_year = ifelse(cohort_year == 2004, Inf, cohort_year))
  
}

data <- make_data2()
plot2 <- data %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) + 
  geom_line(alpha = 1/8, color = "grey") + 
  geom_line(data = data %>% 
              group_by(cohort_year, year) %>% 
              summarize(dep_var = mean(dep_var)),
            aes(x = year, y = dep_var, group = factor(cohort_year),
                color = factor(cohort_year)),
            size = 2) + 
  labs(x = "", y = "Value",  color = "Treatment group   ") + 
  geom_vline(xintercept = 1986, color = '#E41A1C', size = 2) + 
  geom_vline(xintercept = 1992, color = '#377EB8', size = 2) + 
  geom_vline(xintercept = 1998, color = '#4DAF4A', size = 2) + 
  scale_color_brewer(palette = 'Set1') + 
  theme(legend.position = 'bottom',
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  scale_color_manual(labels = c("1986", "1992", "1998", "Never-treated"),
                     values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3"))+
  ggtitle("One draw of the DGP with homogeneous effects across cohorts \n and with a never-treated group")+
  theme(plot.title = element_text(hjust = 0.5, size=12))

plot2 
```
Estimating dynamic treatment effects via TWFE event-study regressions
```{r message=FALSE,results='hide',fig.show='hide'}
keepvars <- c("`rel_year_-5`",  "`rel_year_-4`",  "`rel_year_-3`",  "`rel_year_-2`",
              "rel_year_0", "rel_year_1", "rel_year_2", "rel_year_3", "rel_year_4", "rel_year_5")

run_ES_DiD_never <- function(...) {
  
  data <- make_data2()
  data <- data %>% 
    mutate(rel_year = year - cohort_year) %>% 
    mutate(rel_year = ifelse(rel_year == -Inf, NA, rel_year))%>% 
    dummy_cols(select_columns = "rel_year") %>% 
    mutate(across(starts_with("rel_year_"), ~replace_na(., 0))) %>% 
    mutate(Pre = ifelse((rel_year < -5) * (!is.na(rel_year)), 1, 0),
           Post = ifelse((rel_year > 5) * (!is.na(rel_year)), 1, 0)) %>%
    mutate(Pre = ifelse(is.na(Pre), 0, Pre),
           Post = ifelse(is.na(Post), 0, Post))
  
  mod <- lfe::felm(dep_var ~ Pre + `rel_year_-5` + `rel_year_-4` + `rel_year_-3` + `rel_year_-2` + 
                `rel_year_0` + `rel_year_1` + `rel_year_2` + `rel_year_3` + `rel_year_4` + 
                `rel_year_5` + Post | unit + year | 0 | state, data = data, exactDOF = TRUE)
  # grab the obs we need
  mod2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients)
    )
 es <-
   mod2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(-5:-2, 0:5)) %>% 
    select(t, estimate)
 es
}

data_classical_never <- map_dfr(1:nrep, run_ES_DiD_never)

ES_plot_classical_never <- data_classical_never %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  bind_rows(tibble(t = -1, avg = 0, sd = 0, lower.ci = 0, upper.ci = 0)) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* true_mu, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
  geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
   geom_line(aes(color = 'Estimated Effect'), size = 1) + 
   geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12))+
  ggtitle("TWFE event-study regression with binned end-points")+
    scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())

ES_plot_classical_never
```
```{r message=FALSE,results='hide',fig.show='hide'}
run_ES_DiD_sat_never <- function(...) {

  data <- make_data2()
  data <- data %>% 
    mutate(rel_year = year - cohort_year)
  
  # get the minimum relative year - we need this to reindex
  min_year <- min(data$rel_year * (data$rel_year != -Inf), na.rm = T)
  
  data <- data %>% 
    mutate(rel_year2 = rel_year) %>% 
    mutate(rel_year = rel_year - min_year) %>% 
    dummy_cols(select_columns = "rel_year") %>% 
    select(-("rel_year_-Inf"))
    # make regression formula 
  indics <- paste("rel_year", (1:max(data$rel_year))[-(-1 - min_year)], sep = "_", collapse = " + ")
  keepvars <- paste("rel_year", c(-5:-2, 0:5) - min_year, sep = "_")  
  formula <- as.formula(paste("dep_var ~", indics, "| unit + year | 0 | state"))
  
  mod <- felm(formula, data = data, exactDOF = TRUE)
  
 # grab the obs we need
  mod2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients)
    )
  
 es <-
   mod2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(-5:-2, 0:5)) %>% 
    select(t, estimate)
 es
}

data_sat_never <- map_dfr(1:nrep, run_ES_DiD_sat_never)

ES_plot_sat_never <- data_sat_never %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  bind_rows(tibble(t = -1, avg = 0, sd = 0, lower.ci = 0, upper.ci = 0)) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* true_mu, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
  geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
   geom_line(aes(color = 'Estimated Effect'), size = 1) + 
   geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12))+
  ggtitle("TWFE event-study regression with 'all' leads and lags")+
  scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())

ES_plot_sat_never
```
Using the Callaway and Sant’Anna (202) framework
```{r message=FALSE,results='hide',fig.show='hide'}
run_CS_ny <- function(...) {
  data$cohort_year[data$cohort_year==Inf] <- 0
  mod <- did::att_gt(yname = "dep_var", 
                     tname = "year",
                     idname = "unit",
                     gname = "cohort_year",
                     control_group= "notyettreated",
                     bstrap = FALSE,
                     data = data,
                     print_details = FALSE)
  event_std <- did::aggte(mod, type = "dynamic")
  
  att.egt <- event_std$att.egt
  names(att.egt) <- event_std$egt
  
  # grab the obs we need
  broom::tidy(att.egt) %>% 
    filter(names %in% -5:5) %>% 
    mutate(t = -5:5, estimate = x) %>% 
    select(t, estimate)
}

data_CS_ny <- map_dfr(1:nrep, run_CS_ny)

ES_plot_CS_ny <- data_CS_ny %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* true_mu, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
  geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
   geom_line(aes(color = 'Estimated Effect'), size = 1) + 
   geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12))+
  ggtitle("Event-study-parameters estimated using Callaway and Sant'Anna (2021)\nComparison group: Not-yet-treated units")+
  scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())

ES_plot_CS_ny
```
#### Setup with Heterogeneous Treatment Effects
Visualizing the DGP
```{r message=FALSE,results='hide',fig.show='hide'}
make_data3 <- function(nobs = 1000, 
                      nstates = 40) {
  unit <- tibble(
    unit = 1:nobs,
    state = sample(1:nstates, nobs, replace = TRUE),
    unit_fe = rnorm(nobs, state/5, 1),
    mu = true_mu
  )
  
  # year fixed effects (first part)
  year <- tibble(
    year = 1980:2010,
    year_fe = rnorm(length(year), 0, 1)
  )
  
  treat_taus <- tibble(
    state = sample(1:nstates, nstates, replace = FALSE),
      # place the randomly sampled states into 1\{t \ge g \}G_g
    cohort_year = sort(rep(c(1986, 1992, 1998, 2004), 10))
  )
  
  # full interaction of unit X year 
  expand_grid(unit = 1:nobs, year = 1980:2010) %>% 
    left_join(., unit) %>% 
    left_join(., year) %>% 
    left_join(., treat_taus) %>% 
    # make error term and get treatment indicators and treatment effects
    # Also get cohort specific trends (modify time FE)
    mutate(error = rnorm(nobs*31, 0, 1),
           treat = ifelse((year >= cohort_year)* (cohort_year != 2004), 1, 0),
           mu = ifelse(cohort_year==1992, 2, ifelse(cohort_year==1998, 1, 3)),
           tau = ifelse(treat == 1, mu, 0),
           year_fe = year_fe + 0.1*(year - cohort_year)
    ) %>% 
    # calculate cumulative treatment effects
    group_by(unit) %>% 
    mutate(tau_cum = cumsum(tau)) %>% 
    ungroup() %>% 
    # calculate the dep variable
    mutate(dep_var = (2010 - cohort_year) + unit_fe + year_fe + tau_cum + error) %>%
    # Relabel 2004 cohort as never-treated
    mutate(cohort_year = ifelse(cohort_year == 2004, Inf, cohort_year))
  
}

data <- make_data3()
plot3 <- data %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) + 
  geom_line(alpha = 1/8, color = "grey") + 
  geom_line(data = data %>% 
              group_by(cohort_year, year) %>% 
              summarize(dep_var = mean(dep_var)),
            aes(x = year, y = dep_var, group = factor(cohort_year),
                color = factor(cohort_year)),
            size = 2) + 
  labs(x = "", y = "Value",  color = "Treatment group   ") + 
  geom_vline(xintercept = 1986, color = '#E41A1C', size = 2) + 
  geom_vline(xintercept = 1992, color = '#377EB8', size = 2) + 
  geom_vline(xintercept = 1998, color = '#4DAF4A', size = 2) + 
  scale_color_brewer(palette = 'Set1') + 
  theme(legend.position = 'bottom',
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12)) +
  scale_color_manual(labels = c("1986", "1992", "1998", "Never-treated"),
                     values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3")) +
  ggtitle("One draw of the DGP with heterogeneous treatment effect dynamics across cohorts \n and with a never-treated group")+
  theme(plot.title = element_text(hjust = 0.5, size=12))

plot3 
```
Estimating dynamic treatment effects via TWFE event-study regressions
```{r message=FALSE,results='hide',fig.show='hide'}
keepvars <- c("`rel_year_-5`",  "`rel_year_-4`",  "`rel_year_-3`",  "`rel_year_-2`",
              "rel_year_0", "rel_year_1", "rel_year_2", "rel_year_3", "rel_year_4", "rel_year_5")

run_ES_DiD_never_het <- function(...) {
  data <- make_data3()
  data <- data %>% 
    mutate(rel_year = year - cohort_year) %>% 
    mutate(rel_year = ifelse(rel_year == -Inf, NA, rel_year))%>% 
    dummy_cols(select_columns = "rel_year") %>% 
    mutate(across(starts_with("rel_year_"), ~replace_na(., 0))) %>% 
    # generate pre and post dummies
    mutate(Pre = ifelse((rel_year < -5) * (!is.na(rel_year)), 1, 0),
           Post = ifelse((rel_year > 5) * (!is.na(rel_year)), 1, 0)) %>%
    mutate(Pre = ifelse(is.na(Pre), 0, Pre),
           Post = ifelse(is.na(Post), 0, Post))

  mod <- lfe::felm(dep_var ~ Pre + `rel_year_-5` + `rel_year_-4` + `rel_year_-3` + `rel_year_-2` + 
                `rel_year_0` + `rel_year_1` + `rel_year_2` + `rel_year_3` + `rel_year_4` + 
                `rel_year_5` + Post | unit + year | 0 | state, data = data, exactDOF = TRUE)

# grab the obs we need
  mod2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients)
    )
  
 es <-
   mod2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(-5:-2, 0:5)) %>% 
    select(t, estimate)
 es
}

data_classical_never_het <- map_dfr(1:nrep, run_ES_DiD_never_het)

ES_plot_classical_never_het <- data_classical_never_het %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  bind_rows(tibble(t = -1, avg = 0, sd = 0, lower.ci = 0, upper.ci = 0)) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* 2, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
  geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
   geom_line(aes(color = 'Estimated Effect'), size = 1) + 
   geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12))+
  ggtitle("TWFE event-study regression with binned end-points")+
  scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())

ES_plot_classical_never_het

```

```{r message=FALSE,results='hide',fig.show='hide'}
run_ES_DiD_sat_never_het <- function(...) {
  
  data <- make_data3()
  data <- data %>% 
    mutate(rel_year = year - cohort_year)
  
  # get the minimum relative year - we need this to reindex
  min_year <- min(data$rel_year * (data$rel_year != -Inf), na.rm = T)
  
  # reindex the relative years
  data <- data %>% 
    mutate(rel_year2 = rel_year) %>% 
    mutate(rel_year = rel_year - min_year) %>% 
    dummy_cols(select_columns = "rel_year") %>% 
    select(-("rel_year_-Inf"))
    
  indics <- paste("rel_year", (1:max(data$rel_year))[-(-1 - min_year)], sep = "_", collapse = " + ")
  keepvars <- paste("rel_year", c(-5:-2, 0:5) - min_year, sep = "_")  
  formula <- as.formula(paste("dep_var ~", indics, "| unit + year | 0 | state"))

  mod <- felm(formula, data = data, exactDOF = TRUE)
# grab the obs we need
  mod2 <- tibble(
    estimate = mod$coefficients,
    term1 = rownames(mod$coefficients)
    )
  
 es <-
   mod2 %>% 
    filter(term1 %in% keepvars) %>% 
    mutate(t = c(-5:-2, 0:5)) %>% 
    select(t, estimate)
 es
}

data_sat_never_het <- map_dfr(1:nrep, run_ES_DiD_sat_never_het)

ES_plot_sat_never_het <- data_sat_never_het %>% 
  group_by(t) %>% 
  summarize(avg = mean(estimate),
            sd = sd(estimate),
            lower.ci = avg - 1.96*sd,
            upper.ci = avg + 1.96*sd) %>% 
  bind_rows(tibble(t = -1, avg = 0, sd = 0, lower.ci = 0, upper.ci = 0)) %>% 
  mutate(true_tau = ifelse(t >= 0, (t + 1)* 2, 0)) %>% 
  ggplot(aes(x = t, y = avg)) + 
  geom_ribbon(aes(ymin = lower.ci, ymax = upper.ci), color = "lightgrey", alpha = 0.2) +
  geom_point(color = 'blue', size = 3) + 
   geom_line(aes(color = 'Estimated Effect'), size = 1) + 
   geom_line(aes(x = t, y = true_tau, color = 'True Effect'), linetype = "dashed", size = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = "Estimate") + 
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12))+
  ggtitle("TWFE event-study regression with 'all' leads and lags")+
  scale_color_manual(values = colors) + 
  theme(plot.title = element_text(hjust = 0.5, size=12),
        legend.position = "bottom", 
        legend.title = element_blank())

ES_plot_sat_never_het
```

# Pre-Testing in a DiD Setup using the did Package

```{r message=FALSE,results='hide',fig.show='hide'}
head(dta)
Dtl <- sapply(-(time.periods-1):(time.periods-2), function(l) {
    dtl <- 1*( (dta$period == dta$G + l) & (dta$G > 0) )
    dtl
})
Dtl <- as.data.frame(Dtl)
cnames1 <- paste0("Dtmin",(time.periods-1):1)
colnames(Dtl) <- c(cnames1, paste0("Dt",0:(time.periods-2)))


data <- cbind.data.frame(dta, Dtl)
row.names(data) <- NULL
head(data)

library(plm)

es <- plm(Y ~ Dtmin3 + Dtmin2 + Dt0 + Dt1 + Dt2, 
          data=data, model="within", effect="twoways",
          index=c("id","period"))

summary(es)

coefs1 <- coef(es)
ses1 <- sqrt(diag(summary(es)$vcov))
idx.pre <- 1:(time.periods-2)
idx.post <- (time.periods-1):length(coefs1)
coefs <- c(coefs1[idx.pre], 0, coefs1[idx.post])
ses <- c(ses1[idx.pre], 0, ses1[idx.post])
exposure <- -(time.periods-1):(time.periods-2)

cmat <- data.frame(coefs=coefs, ses=ses, exposure=exposure)

library(ggplot2)

ggplot(data=cmat, mapping=aes(y=coefs, x=exposure)) +
  geom_line(linetype="dashed") +
  geom_point() + 
  geom_errorbar(aes(ymin=(coefs-1.96*ses), ymax=(coefs+1.96*ses)), width=0.2) +
  ylim(c(-2,5)) +
  theme_bw()
```

```{r message=FALSE,results='hide',fig.show='hide'}
did_att_gt <- att_gt(yname="Y",
                     tname="period",
                     idname="id",
                     gname="G",
                     data=data,
                     bstrap=FALSE,
                     cband=FALSE)
summary(did_att_gt)
ggdid(did_att_gt)

did_es <- aggte(did_att_gt, type="dynamic")
ggdid(did_es)
```


I can't solve code  problems in Pitfall: Selective Treatment Timing.The result is same with when without- selective is.

#### Conditional Moment Tests

# Writing Extensions to the did Package
#### DiD with Anticipation
Computing Treatment Effects under DiD with Anticipatio
```{r message=FALSE,results='hide',fig.show='hide'}
time.periods <- 5
st<-reset.sim()
st$te <- 0
st$te.e <- c(-1,rep(1,time.periods-1))
st$bett <-st$betu <- rep(0,time.periods)
set.seed(12345)
dta <- build_sim_dataset(st)
dta$G <- ifelse(dta$G==0, 0, dta$G+1)
dta$G <- ifelse(dta$G==6, 0, dta$G)
nrow(dta)
head(dta)
```

```{r message=FALSE,results='hide',fig.show='hide'}
attgt.ignoredip <- att_gt(yname = "Y",
                          tname = "period",
                          idname = "id",
                          gname = "G",
                          xformla = ~1,
                          data = dta,
                          )
summary(attgt.ignoredip)
p <- ggdid(aggte(attgt.ignoredip, "dynamic"))
library(ggplot2)
truth <- cbind.data.frame(e = seq(-3,2), att.e = c(0,0,-1,1,1,1))
p <- p + geom_line(data = truth, aes(x = e, y = att.e), inherit.aes = FALSE, color = "blue")
p <- p + geom_point(data = truth, aes(x = e, y = att.e), inherit.aes = FALSE, color = "blue")
p
```

```{r message=FALSE,results='hide',fig.show='hide'}
compute.attgt <- function(dta) {
  groups <- unique(dta$G)
  time.periods <- unique(dta$period)
  groups <- sort(groups)[-1]
  time.periods <- sort(time.periods)[-c(1,2)]
  time.periods <- time.periods[-length(time.periods)]
  attgt.list <- list()
  counter <- 1

  for (g in groups) {
    main.base.period <- g - 2
    
    for (tp in time.periods) {
      if (tp < g) {
        base.period <- tp - 2
      } else {
        base.period <- main.base.period
      }
      this.data <- subset(dta, G==g | G==0)

      this.data <- subset(this.data, period==tp | period==base.period)
      Ypost <- subset(this.data, period==tp)$Y
      Ypre <- subset(this.data, period==base.period)$Y

      G <- 1*(subset(this.data, period==tp)$G == g)
      attgt <- DRDID::reg_did_panel(Ypost, Ypre, G, covariates=NULL)$ATT
      attgt.list[[counter]] <- list(att=attgt, group=g, time.period=tp)
      counter <- counter+1
    }
  }

  attgt.results <- do.call("rbind.data.frame", attgt.list)
  attgt.results$e <- attgt.results$time.period - attgt.results$group
  # (will be used as weights)
  n.group <- sapply(groups, function(gg) nrow(subset(dta, G==gg)))
  ngroup.mat <- cbind(groups, n.group)
  attgt.results <- merge(attgt.results, ngroup.mat, by.x = "group", by.y = "groups")
  eseq <- unique(attgt.results$e) 
  eseq <- sort(eseq)
  att.e <- c()
  counter <- 1
  for (this.e in eseq) {
    res.e <- subset(attgt.results, e==this.e)
    res.e$weight <- res.e$n.group / sum(res.e$n.group)
    att.e[counter] <- sum(res.e$att * res.e$weight)
    counter <- counter+1
  }
  dyn.results <- cbind.data.frame(e = eseq, att.e = att.e)
  return(list(attgt.results=attgt.results[,c("group","att","time.period")],
              dyn.results=dyn.results))
}
```

```{r message=FALSE,results='hide',fig.show='hide'}
anticipation.results <- compute.attgt(dta)
anticipation.results
```
Frankly,because of  simulated data, I can't deal with the code "BMisc::blockBootSample(dta, "id")"  about nonparametric bootstrap in the final act.